Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-24 Scripts/Initial_Analysis.Rmd
finalized supplemental plots

This results only shows the average percentage change in proportion of all speecies within an EEZ without relationship with neighbors

@@

This function estimates the total change in MCP proportion of each species for each EEZ. It looses the connection with neighbors as you only know for x species how much is the proportion changing.

@@

The next step is to summarize all species per eez so our results shows average change of all species within an EEZ towards a neighbour.

@@

# Neighbor list and their respective id (see chunk 3)
Neighbours <- my_path("D", extra_path = "Spatial/", name="Neighbours_eez_id.csv", read = TRUE)

@@

# Species catch trend (from FishForVisa)

# Catch_trend <- my_path("D","Species","Catch_trend.csv", read = T) %>% 
#   clean_names() %>% 
#   filter(taxon_key %in% Taxon_list_emer) %>% 
#   rename(sau_fishing_entity = territory) %>% 
#   left_join(Fishing_names,
#             by = "sau_fishing_entity") %>% 
#   filter(status != "No Trend") %>% 
#   mutate(category = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
#                          ifelse(status == "Max Exploited","Category B",
#                                 ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
#                          )
#          )
#   )

@@

# Read proportion results
suppressMessages(
  Prop_results <- PropChange(Taxon_list, links="y") %>%
    filter(!is.na(eez_neighbour)) %>%
    mutate(per_mid_plot =ifelse(per_mid >= 100, 100,
                                ifelse(per_mid <= -100,-100,per_mid)
    ),
    per_early_plot =ifelse(per_early >= 100, 100,
                           ifelse(per_early <= -100,-100,per_early)
    )
    )
)
# For dat availability
# write_csv(prop_results,
# "proportion_change_2005.csv")

@@

@@

  map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    # geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x = -14012580,
             y = -8357450,
             label = "Transboundary fish revenue (%)",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text",
             x = c(-3812580,-4500,3800000,7700000,11512580),
             y = -8400000,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100),
             color="black",
             size=4,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # # Set ToE labels
    annotate("text",
             # x =-150,
             # y = -85,
             x = -13012580,
             y = -9657450,
             label = "Average year of range shift",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text",
             # x = c(-79,-39,2,42,81),
             # y = -85,
             x = c(-4412580,-430000,3410000,7300000,11312580),
             y = -9657450,
             # label = seq(2100,2000,-25), # original
             label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black",
             size=4,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # # Set No emergence label
    annotate("text",
             # x =110,
             # y = -77,
             x = 13000000,
             y = -9000000,
             label = "No shift",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("rect", 
             xmin = 15500000, 
             xmax = 16500000, 
             ymin = -8600000, 
             ymax = -9300000,
             fill = "lightblue") +
    scale_fill_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c("","","","","")#,
                       # direction = -1
    ) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(
      legend.box.margin = margin(t = -61,l = 180),
      legend.text = element_blank(),
      legend.background = element_blank(),
      legend.key.width = unit(5, "line")
    )

>>>>

This results only shows the average percentage change in proportion of all species within an EEZ without relationship with neighbours

@@

This function estimates the total change in MCP proportion of each species for each EEZ. It looses the connection with neighbours as you only know for x species how much is the proportion changing.

@@

The next step is to summarize all species per EEZ so our results shows average change of all species within an EEZ towards a neighbour.

@@

# Neighbor list and their respective id from Palacios-Abrantes et al 2020 (FishForVisa)
Neighbours <- my_path("D", extra_path = "Spatial/", name="Neighbours_eez_id.csv", read = TRUE)

@@

@@

# Read proportion results
suppressMessages(
  Prop_results <- PropChange(Taxon_list, links="y") %>%
    filter(!is.na(eez_neighbour)) %>%
    mutate(per_mid_plot =ifelse(per_mid >= 100, 100,
                                ifelse(per_mid <= -100,-100,per_mid)
    ),
    per_early_plot =ifelse(per_early >= 100, 100,
                           ifelse(per_early <= -100,-100,per_early)
    )
    )
)
# For dat availability
# write_csv(Prop_results,
# "Data/ssr_data.csv")

@@

# Write data file for Github

toe_data <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Exploited_spp_list) %>% 
            select(taxon_key,taxon_name,common_name,everything(),-genus,-species)

write_csv(toe_data, "./Data/toe_data.csv")

@@

  map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation, 
                color = participation),
            # color =  "white",
            size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", 
            # color =  "white",
            size = 0.1) +
    # geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x = -14012580,
             y = -8357450,
             label = "Transboundary fish revenue (%)",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text",
             x = c(-3812580,-4500,3800000,7700000,11512580),
             y = -8400000,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100),
             color="black",
             size=4,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # # Set ToE labels
    annotate("text",
             # x =-150,
             # y = -85,
             x = -13012580,
             y = -9657450,
             label = "Average year of range shift",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text",
             # x = c(-79,-39,2,42,81),
             # y = -85,
             x = c(-4412580,-430000,3410000,7300000,11312580),
             y = -9657450,
             # label = seq(2100,2000,-25), # original
             label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black",
             size=4,
             angle=0,
             # fontface="bold",
             hjust=0) +
    # # Set No emergence label
    annotate("text",
             # x =110,
             # y = -77,
             x = 13000000,
             y = -9000000,
             label = "No shift",
             color="black",
             size=5,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("rect", 
             xmin = 15500000, 
             xmax = 16500000, 
             ymin = -8600000, 
             ymax = -9300000,
             fill = "lightblue") +
    scale_fill_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c("","","","","")#,
                       # direction = -1
    ) +
    scale_color_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       labels = c("","","","","")#,
                       # direction = -1
    ) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(
      legend.box.margin = margin(t = -61,l = 180),
      legend.text = element_blank(),
      legend.background = element_blank(),
      legend.key.width = unit(5, "line")
    )
